---
title: "Saras Replication - Preprocessed Data - Figures Tables ReRun"
author: "Sara Murphy"
date: "2026-03-22"
output: html_document
---

``````{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,      # hide all code
  message = FALSE,   # hide messages
  warning = FALSE    # hide warnings
)
``````


## Replication "Generate Figures and Tables" R Script - Pre-Processed Data

#Load Data - FULL SPEECHES DATASET
Loaded the data, found key columns.

Does not contain the raw text files. Contains the ideology scores and flesh.grade scores

Complexity column = FK score
PC = progressive vs conservative (social)
LR = left vs right (economic)
data.set = particular data set (EU, parliament speeches, congress)

```{r}
#################################################################
# Script to generate Figures and Tables in:
# Liberals Lecture, Conservatives Communicate:
# analyzing complexity and ideology in 381,609 speeches
# Martijn Schoonvelde, Anna Brosius, Gijs Schumacher, Bert Bakker
# Contact: mschoonvelde@gmail.com
#################################################################

###############
#load libraries
###############

rm(list=ls())
library(stringr)
library(stargazer)
library(ggplot2)
library(stringr)
library(merTools)
#library(hrbrthemes) could not install
library(devtools)
#library(ggflags) could not install
library(stringr)
library(plyr)

#load data - from Git Hub Repository
library(tidyverse)
library(here)

here()
getwd()
file.exists(here("dataverse", "phase1", "speeches.RData"))

temp_env <- new.env()
load(here("dataverse", "phase1", "speeches.RData"), envir = temp_env)
ls(temp_env)

speeches <- temp_env$speeches

View(speeches)      # spreadsheet view
head(speeches) #first few rows
str(speeches)       # structure (VERY important)
dim(speeches)       # rows × columns
names(speeches)     # variable names

```


```{r}
# Run regression analyses -------------------------------------------------
vars1 <- as.formula(scale(complexity) ~ scale(lr) + scale(pc) + year2 + office)

reg.output <- list()
reg.output[[1]] <- lm(vars1, data=speeches, subset=country=="DK" & data.set=="congress speeches")
reg.output[[2]] <- lm(vars1, data=speeches, subset=country=="NL" & data.set=="congress speeches")

reg.output[[3]] <- lm(vars1, data=speeches, subset=country=="Germany" & data.set=="parliamentary speeches")
reg.output[[4]] <- lm(vars1, data=speeches, subset=country=="Spain"  & data.set=="parliamentary speeches") 
reg.output[[5]] <- lm(vars1, data=speeches, subset=country=="UK" & data.set=="parliamentary speeches")
reg.output[[6]] <- lm(vars1, data=speeches, subset=country=="Sweden" & data.set=="parliamentary speeches")
reg.output[[7]] <-lm(vars1, data=speeches, subset=country=="Netherlands" & data.set=="parliamentary speeches") 

vars2 <- as.formula(scale(complexity) ~ scale(lr) + scale(pc))
reg.output[[8]] <- lm(vars2, data=speeches, subset=data.set=="PM speeches")
```


```{r}
#figures progressive conservative (fig 2a)
####################################################

#create dataframe with model results to be plotted
coefs <- unlist(lapply(reg.output, function(x) x$coefficients[3]))
se <- unlist(lapply(reg.output, function(x) sqrt(diag(vcov(x)))[3]))
min <- coefs - 1.96*se
max <- coefs + 1.96*se
names <- c("Party congresses DNK", "Party congresses NLD", "Parliament GER", "Parliament ESP", "Parliament GBR", "Parliament SWE","Parliament NLD", "Heads of Government") 
plot.data <- data.frame(names,coefs,se,min,max)
order.names <- c(8,2,1,7,6,5,4,3)
plot.data <- plot.data[order.names,]
plot.data$names <- factor(plot.data$names, levels=plot.data$names)
plot.data$institution <- c(rep("Congress and Heads of Government","3"), rep("Parliament","5"))
plot.data$institution <- factor(plot.data$institution, levels = c("Parliament", "Congress and Heads of Government"))


#create plot
coef.plot2a <- ggplot(plot.data[], aes(x=names, y=coefs)) +
  geom_point(size = 1) +
  geom_errorbar(ymin=plot.data$min[],ymax=plot.data$max[], width=.1) +
  coord_flip() + 
  ylab("Effect of lib-cons ideology") +
  xlab("") + 
  geom_hline(yintercept=0) +
  theme_minimal() +
  facet_wrap(institution~., scales="free",nrow = 2) +  ylim(c(-.25,0.025)) + theme(panel.spacing = unit(2, "lines"))

#changed to PDF, fixed code with filename=
ggsave(
  filename = "fig2a.pdf",
  plot = coef.plot2a,
  dpi = 300
)

print(coef.plot2a)
```


```{r}
#figure left-right (fig 2b)
###############################

#create dataframe with model results to be plotted
coefs <- unlist(lapply(reg.output, function(x) x$coefficients[2]))
se <- unlist(lapply(reg.output, function(x) sqrt(diag(vcov(x)))[2]))
min <- coefs - 1.96*se
max <- coefs + 1.96*se
names <- c("Party congresses DNK", "Party congresses NLD", "Parliament GER", "Parliament ESP", "Parliament GBR", "Parliament SWE","Parliament NLD", "Heads of Government") 
plot.data <- data.frame(names,coefs,se,min,max)
order.names <- c(8,2,1,7,6,5,4,3)
plot.data <- plot.data[order.names,]
plot.data$names <- factor(plot.data$names, levels=plot.data$names)
plot.data$institution <- c(rep("Congress and Heads of Government","3"), rep("Parliament","5"))
plot.data$institution <- factor(plot.data$institution, levels = c("Parliament", "Congress and Heads of Government"))

#create plot
coef.plot2b <- ggplot(plot.data, aes(x=names, y=coefs)) +
  geom_point(size = 1) +
  geom_errorbar(ymin=plot.data$min,ymax=plot.data$max, width=.1) +
  coord_flip() + 
  ylab("Effect of left-right ideology") +
  xlab("") + 
  geom_hline(yintercept=0) +
  theme_minimal() +
  facet_wrap(institution~., scales="free",nrow = 2) +  ylim(c(-.20,0.11)) + theme(panel.spacing = unit(2, "lines"))

ggsave(
  filename = "fig2b.pdf",
  plot = coef.plot2b,
  dpi = 300
)

print(coef.plot2b)
```


```{r}
#figure government - opposition (b1 appendix)
#############################################

#create dataframe with model results to be plotted
coefs <- unlist(lapply(reg.output, function(x) x$coefficients[5]))[-8]
se <- unlist(lapply(reg.output, function(x) sqrt(diag(vcov(x)))[5]))[-8]
min <- coefs - 1.96*se
max <- coefs + 1.96*se
names <- c("Party congresses DNK", "Party congresses NLD", "Parliament GER", "Parliament ESP", "Parliament GBR", "Parliament SWE","Parliament NLD")  
plot.data <- data.frame(names,coefs,se,min,max)
order.names <- c(2,1,7,6,5,4,3)
plot.data <- plot.data[order.names,]
plot.data$names <- factor(plot.data$names, levels=plot.data$names)
plot.data$institution <- c(rep("Congress","2"), rep("Parliament","5"))
plot.data$institution <- factor(plot.data$institution, levels = c("Parliament", "Congress"))

#create plot
coef.plotb1 <- ggplot(plot.data, aes(x=names, y=coefs)) +
  geom_point(size = 1) +
  geom_errorbar(ymin=plot.data$min,ymax=plot.data$max, width=.1) +
  coord_flip() + 
  ylab("Effect of government status") + geom_hline(yintercept=0) +
  xlab("") + facet_wrap(institution~., scales="free",nrow = 2) +
  theme_minimal() + theme(panel.spacing = unit(2, "lines")) +  ylim(c(-.075,0.30))

ggsave(
  filename = "figb1.pdf",
  plot = coef.plotb1,
  dpi = 300
)

print(coef.plotb1)
```


```{r}
#figure time series complexity
#A: congress speeches
#B: parl speech
##############################
speeches.subset <- speeches[-which(speeches$data.set=="PM speeches"),]
speeches.subset$id <- ifelse(speeches.subset$country=="NL", "NLD",
                      ifelse(speeches.subset$country=="DK", "DNK",
                      ifelse(speeches.subset$country=="Germany", "GER",
                      ifelse(speeches.subset$country=="UK", "GBR",
                      ifelse(speeches.subset$country=="Netherlands", "NLD",
                      ifelse(speeches.subset$country=="Spain", "ESP",
                      ifelse(speeches.subset$country=="Sweden", "SWE",NA)))))))

speeches.subset$year <- as.numeric(speeches.subset$year)
speeches.subset$complexity[speeches.subset$country=="Spain"] <- speeches.subset$complexity[speeches.subset$country=="Spain"]-10
speeches.parl <- speeches.subset[speeches.subset$data.set=="parliamentary speeches",]  
speeches.congress <- speeches.subset[speeches.subset$data.set=="congress speeches",]  

time.plot.parl <- ggplot(speeches.parl,aes(x=year, y=complexity)) +
  geom_smooth(se=FALSE, colour="red") + 
  facet_wrap(~id, nrow=1) +
  scale_x_continuous(breaks=c(1990,2000,2010), labels=c("'90", "'00", "'10")) + 
  ylab("Complexity") +
  xlab("") + 
  theme_minimal() 

time.plot.congress <- ggplot(speeches.congress,aes(x=year, y=complexity)) +
  geom_smooth(se=FALSE, colour="red") + 
  facet_wrap(~id, nrow=1) +
  ylab("Complexity") +
  scale_x_continuous(breaks=c(1960,1980,2000), labels=c("'60", "'80", "'00")) + 
  xlab("") + 
  theme_minimal()  

ggsave(
  filename = "fig2c.pdf",
  plot = time.plot.parl,
  dpi = 300
)

print(time.plot.parl)

ggsave(
  filename = "fig2d.pdf",
  plot = time.plot.congress,
  dpi = 300
)

print(time.plot.congress)
```


```{r}
## Fixed-effect models
vars3 <- as.formula(complexity ~ lr + pc + year2 + office + factor(speaker))
reg.output.fixed <- list()
reg.output.fixed[[1]]  <- lm(vars3, data=speeches, subset=country=="DK" & data.set=="congress speeches")
reg.output.fixed[[2]]  <- lm(vars3, data=speeches, subset=country=="NL" & data.set=="congress speeches")

reg.output.fixed[[3]] <- lm(vars3, data=speeches, subset=country=="Germany" & data.set=="parliamentary speeches")
reg.output.fixed[[4]] <- lm(vars3, data=speeches, subset=country=="Spain"  & data.set=="parliamentary speeches") 
reg.output.fixed[[5]] <- lm(vars3, data=speeches, subset=country=="UK" & data.set=="parliamentary speeches")
reg.output.fixed[[6]] <- lm(vars3, data=speeches, subset=country=="Sweden" & data.set=="parliamentary speeches")
reg.output.fixed[[7]] <-lm(vars3, data=speeches, subset=country=="Netherlands" & data.set=="parliamentary speeches")
```


```{r}
#plot data
##########

#create dataframe with model results to be plotted
coefs <- unlist(lapply(reg.output.fixed, function(x) coef(x)[3]))
se <- unlist(lapply(reg.output.fixed, function(x) sqrt(diag(vcov(x)))[3]))
min <- coefs - 1.96*se
max <- coefs + 1.96*se
names <- c("Party congresses DNK", "Party congresses NLD", "Parliament GER", "Parliament ESP", "Parliament GBR", "Parliament SWE","Parliament NLD") 
plot.data <- data.frame(names,coefs,se,min,max)
order.names <- c(2,1,7,6,5,4,3)
plot.data <- plot.data[order.names,]
plot.data$names <- factor(plot.data$names, levels=plot.data$names)

#create plot
coef.plot3 <- ggplot(plot.data, aes(x=names, y=coefs)) +
  geom_point() + 
  geom_errorbar(ymin=plot.data$min,ymax=plot.data$max, width=.1) +
  coord_flip() + 
  ylab("Fixed effect of conservatism") +
  xlab("") + 
  geom_hline(yintercept=0) +
  theme_minimal()


ggsave(
  filename = "fig3a.pdf",
  plot = coef.plot3,
  dpi = 300
)

print(coef.plot3)

```


```{r}
# #congress speech --------------------------------------------------------
setwd("~/Documents/GitHub/Text Analysis Course/Replication Project/dataverse_files-2")
temp_env <- new.env()
load("congressspeech.RData", envir = temp_env)

ls(temp_env)   # shows "speeches"

congressspeech <- temp_env$speeches

View(congressspeech)
head(congressspeech)
str(congressspeech)
dim(congressspeech)
names(congressspeech)

congress.speech <- congressspeech

# scale variables
congress.speech$scale.complexity <- scale(congress.speech$Flesch.Kincaid)
congress.speech$scale.pc<- scale(congress.speech$pc)

selection <- congress.speech[congress.speech$party=="S" | congress.speech$party=="VVD",]
selection$party <- factor(selection$party, labels=c("Social Democratic Party\n(DK)","Liberal Party\n(NL)"))

selection.plot <- ggplot(selection,aes(x=year, y=scale.complexity)) +
  geom_smooth(aes(colour="blue")) +
  geom_smooth(aes(x=selection$year, y=selection$scale.pc, colour="red")) +
  theme_minimal() +
  ylab("Standardized values") +
  xlab("") +
  facet_grid(party~., labeller = label_value) + 
  theme(legend.position="bottom") + scale_colour_manual(name="", values=c("blue", "red"), labels = c("complexity", "ideology")) 

ggsave(
  filename = "fig3b.pdf",
  plot = selection.plot,
  dpi = 900
)

print(selection.plot)
```


```{r}
# # EU Speech -------------------------------------------------------------
setwd("~/Documents/GitHub/Text Analysis Course/Replication Project/dataverse_files-2")
temp_env <- new.env()
load("euspeech.RData", envir = temp_env)

ls(temp_env)   # shows "speeches"

euspeech <- temp_env$speeches

View(euspeech)
head(euspeech)
str(euspeech)
dim(euspeech)
names(euspeech)

eu.speech <-  euspeech

example1 <- ddply(eu.speech, "speaker", summarise, 
              mean=mean(complexity, na.rm=TRUE), 
              SD=sd(complexity, na.rm=TRUE),
              N=length(speaker))
example1$se <- example1$SD / sqrt(example1$N)
example1$min <- example1$mean - 1.96*example1$se
example1$max <- example1$mean + 1.96*example1$se

example1 <- example1[c(4,6,8,10),] # select only cameron, brown, rajoy & zapatero
```


```{r}
# Parlspeech
setwd("~/Documents/GitHub/Text Analysis Course/Replication Project/dataverse_files-2")
temp_env <- new.env()
load("parlspeech.RData", envir = temp_env)

ls(temp_env)   # shows "speeches"

parlspeech <- temp_env$speeches

View(parlspeech)
head(parlspeech)
str(parlspeech)
dim(parlspeech)
names(parlspeech)

parl.speech <-  parlspeech

# Checking Speaker Names
unique(parlspeech$speaker)

table(parlspeech[parlspeech$speaker %in% c(
  "David Cameron","Gordon Brown","rodriguez zapatero","rajoy brey"
), "speaker"])

table(parlspeech[parlspeech$speaker %in% c(
  "Joseph Fischer","Nick Clegg","JIMMIE ÅKESSON","Wilders"
), "speaker"])

#Sara had to fix. Check names of candidates in dataset rather than official name

#missing example1 - Sara had to add
parl.speech <-  parlspeech[parlspeech$speaker%in%c("David Cameron","Gordon Brown","rodriguez zapatero","rajoy brey"),]
example1 <- ddply(parl.speech, "speaker", summarise, 
                 mean=mean(flesh.grade, na.rm=TRUE), 
                 SD=sd(flesh.grade, na.rm=TRUE), #fix - to flesh.grade
                 N=length(speaker)) #fix
example1$N=as.numeric(example1$N)
example1$se <- example1$SD / sqrt(example1$N)
example1$min <- example1$mean - 1.96*example1$se
example1$max <- example1$mean + 1.96*example1$se

#example 2
parl.speech <-  parlspeech[parlspeech$speaker%in%c("Joseph Fischer","Nick Clegg"," JIMMIE ÅKESSON ","Wilders"),]
example2 <- ddply(parl.speech, "speaker", summarise, 
                 mean=mean(flesh.grade, na.rm=TRUE), 
                 SD=sd(flesh.grade, na.rm=TRUE), #fix - to flesh.grade
                 N=length(speaker)) #fix
example2$N=as.numeric(example2$N)
example2$se <- example2$SD / sqrt(example2$N)
example2$min <- example2$mean - 1.96*example2$se
example2$max <- example2$mean + 1.96*example2$se

#row bind. Fix: Need to make names more precise
example <- parlspeech %>%
  filter(speaker %in% c(
    "David Cameron",
    "Gordon Brown",
    "rodriguez zapatero",
    "rajoy brey",
    " JIMMIE ÅKESSON ",
    "Joseph Fischer",
    "Nick Clegg",
    "Wilders"
  )) %>%
  
  mutate(speaker_short = case_when(
    speaker == "David Cameron" ~ "Cameron",
    speaker == "Gordon Brown" ~ "Brown",
    speaker == "rodriguez zapatero" ~ "Zapatero",
    speaker == "rajoy brey" ~ "Rajoy",
    speaker == " JIMMIE ÅKESSON " ~ "Åkesson",
    speaker == "Joseph Fischer" ~ "Fischer",
    speaker == "Nick Clegg" ~ "Clegg",
    speaker == "Wilders" ~ "Wilders"
  ))

example <- rbind(example1,example2)
example$speaker <- c("Cameron", "Brown", "zapatero", "rajoy", "ÅKESSON", "Fischer", "Clegg", "Wilders")
example$prog <- c(0,1,1,0,0,1,1,0)
order <- c(5,8,7,6,4,3,1,2)
example <- example[order,]
example$speaker <- factor(example$speaker, levels=example$speaker)
example$country <- c("se","nl","gb", "de", "es", "es", "gb", "gb")
example$label <- c("UK","UK","ES","ES","DE","UK","NL","SE")



desc.plot <- ggplot(example, aes(x=speaker, y=mean, fill=factor(prog), country=country)) + 
  geom_bar(stat="identity") + 
  geom_errorbar(ymin=example$min,ymax=example$max, width=.2) + 
geom_text(aes(y = max + 0.5, label = country),
          hjust = -0.2,
          size = 4)+
  coord_flip() + 
  xlab("") +
  ylab("Mean Complexity") + 
  scale_fill_manual(values=c("#56B4E9","#E69F00")) + #"#999999"
  theme_minimal() + 
  ylim(c(0,30)) + 
  guides(fill=FALSE)


ggsave(
  filename = "fig1.pdf",
  plot = desc.plot,
  dpi = 900
)

print(desc.plot)

```