---
title: "Replication Paper - Sara - Unprocessed Sample Speech Data"
author: "Sara Murphy"
date: "2026-03-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,      # hide all code
  message = FALSE,   # hide messages
  warning = FALSE    # hide warnings
)
```

## Sara's Attempt - Liberals Lecture, Conservatives Communicate

## REPLICATION OF UNPROCESSED DATA

#Load Data - PARLIAMENT SPEECHES
Loaded the data, found key columns.

# 1) GBR - GREAT BRITAIN - HOUSE OF COMMONS 
3,873 speeches


```{r}
library(tidyverse)
library(here)

temp_env <- new.env()
load(here("dataverse", "phase2a", "HouseofCommons_Sample.Rdata"), envir = temp_env)
ls(temp_env)

#rename to Parliament speeches
gbr_sample <- temp_env$hoc.corpus.sample

# Dataset is called speeches
View(gbr_sample)      # spreadsheet view
head(gbr_sample)      # first rows
str(gbr_sample)       # structure (VERY important)
dim(gbr_sample)       # rows × columns
names(gbr_sample)     # variable names


```
# 2) ESP - SPAIN - CONGRESSO
3,270

```{r}
temp_env <- new.env()
load(here("dataverse", "phase2a", "Congresso_Sample.Rdata"), envir = temp_env)
ls(temp_env)

#rename to Parliament speeches
esp_sample <- temp_env$cong.corpus.sample

# Dataset is called speeches
View(esp_sample)      # spreadsheet view
head(esp_sample)      # first rows
str(esp_sample)       # structure (VERY important)
dim(esp_sample)       # rows × columns
names(esp_sample)     # variable names

```
# 3) GER - GERMANY - BUNDESTAG
4,960

```{r}
temp_env <- new.env()
load(here("dataverse", "phase2a", "Bundestag_Sample.Rdata"), envir = temp_env)
ls(temp_env)

#rename to Parliament speeches
ger_sample <- temp_env$bt.corpus.sample

# Dataset is called speeches
View(ger_sample)      # spreadsheet view
head(ger_sample)      # first rows
str(ger_sample)       # structure (VERY important)
dim(ger_sample)       # rows × columns
names(ger_sample)     # variable names

```
# 4) NLD - NETHERLANDS - TWEEDE KAMER
3,865
Random sample?

```{r}
temp_env <- new.env()
load(here("dataverse", "phase2a", "TweedeKamer_Sample.Rdata"), envir = temp_env)
ls(temp_env)

#rename to Parliament speeches
nld_sample <- temp_env$tk.corpus.sample

# Dataset is called speeches
View(nld_sample)      # spreadsheet view
head(nld_sample)      # first rows
str(nld_sample)       # structure (VERY important)
dim(nld_sample)       # rows × columns
names(nld_sample)     # variable names

```
#Load Data - EU SPEECHES
Loaded the data, found key columns.

```{r}
library(tidyverse)
library(here)

eu_sample <- read_csv(here("dataverse", "phase2b", "EUSPeech_Validation.csv"))


# Dataset is called speeches
View(eu_sample)      # spreadsheet view
head(eu_sample)      # first rows
str(eu_sample)       # structure (VERY important)
dim(eu_sample)       # rows × columns
names(eu_sample)     # variable names

```
#Load Data - CONGRESS SPEECHES - DUTCH/NETHERLANDS
Loaded the data, found key columns.

```{r}
library(tidyverse)
library(here)

congress_nld_sample <- read_csv(here("dataverse", "phase2b", "Congress_Dutch_Validation.csv"))

# Dataset is called speeches
View(congress_nld_sample)      # spreadsheet view
head(congress_nld_sample)      # first rows
str(congress_nld_sample)       # structure (VERY important)
dim(congress_nld_sample)       # rows × columns
names(congress_nld_sample)     # variable names

```

# REPLICATE DV - Linguistic Complexity Flesch Grade

# 1) GBR

```{r}
library(quanteda)
library(quanteda.textstats)

# create corpus
corp_gbr <- corpus(gbr_sample, text_field = "text")

# compute readability
readability_scores <- textstat_readability(
  corp_gbr,
  measure = "Flesch.Kincaid"
)

# add score back to original data
gbr_sample$complexity <- readability_scores$Flesch.Kincaid
head(readability_scores)
head(gbr_sample$complexity)
summary(gbr_sample$complexity)


# if your texts are in a data frame called df with column text
read_out <- textstat_readability(
  gbr_sample$text,
  measure = "Flesch.Kincaid",
  intermediate = TRUE
)
names(read_out)
head(read_out)

# Extract Word, Word Count and Syllables - Quanteda
gbr_sample$word_count_quanteda     <- read_out$W
gbr_sample$sentence_count_quanteda <- read_out$St
gbr_sample$syllables_quanteda      <- read_out$Sy

# Calculate Differences
gbr_sample <- gbr_sample %>%
  mutate(
    word_diff_q      = word_count_quanteda - length,
    sentence_diff_q  = sentence_count_quanteda - sentences,
    syllable_diff_q  = syllables_quanteda - syllables
  )

#Correlations 
cor(gbr_sample$length, gbr_sample$word_count_quanteda, use = "complete.obs")
cor(gbr_sample$sentences, gbr_sample$sentence_count_quanteda, use = "complete.obs")
cor(gbr_sample$syllables, gbr_sample$syllables_quanteda, use = "complete.obs")
```


```{r}
# Graph
ggplot(gbr_sample, aes(x = length, y = word_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - GBR")

ggplot(gbr_sample, aes(x = sentences, y = sentence_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - GBR")

ggplot(gbr_sample, aes(x = syllables, y = syllables_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Syllable Count: Original vs Replicated - GBR")

gbr_sample$country <- "UK"

saveRDS(gbr_sample, "gbr_sample_edited.rds")
```

#GBR - Assess Replication to Original 

You can say something like:
“The replicated Flesch-Kincaid scores are highly correlated with the original measures (r = X.XX).”
“The mean difference between measures is small (M = X.XX, SD = X.XX).”
“Visual inspection (Figure X) shows strong alignment along the 45-degree line.”

✅ What your plot shows (big picture)
1. Strong positive relationship
The points form a tight upward-sloping cloud
This means your replicated scores track the authors’ scores closely
👉 Interpretation:
✔ You are capturing the same underlying signal of complexity
2. Close to the 45° line (red line)
The red line represents perfect replication (your score = their score)
Most points are clustered near it
👉 Interpretation:
✔ Your implementation is largely correct
✔ No major coding mistake
⚠️ What’s not perfect (and very important for your paper)
3. Systematic deviation at higher values
At higher Flesch grades (≈ 13–20):
Your points tend to sit above the line
👉 This means:
You are overestimating complexity for harder texts
4. Increasing spread (heteroskedasticity)
The scatter widens as scores increase
👉 Interpretation:
Your method is less precise for complex speeches
Likely due to:
sentence splitting differences
syllable counting differences
punctuation handling
5. Outliers
A few points are far above the line (e.g., 25–30)
👉 These are likely:
badly parsed speeches
very short texts
encoding/tokenization issues
📊 What this means for your replication
✔ What you can confidently claim:
High convergent validity
Strong correlation with original measure
Correct implementation of Flesch-Kincaid formula
⚠️ What you should acknowledge:
Small but systematic differences
Especially for high-complexity texts

```{r}
# Calculate Differences - My Complexity to Flesch Grade Score of Authors
gbr_sample$difference <- gbr_sample$complexity - gbr_sample$flesh.grade
gbr_sample$abs_diff <- abs(gbr_sample$difference)

summary(gbr_sample$difference)
mean(gbr_sample$difference, na.rm = TRUE)
sd(gbr_sample$difference, na.rm = TRUE)
mean(gbr_sample$abs_diff, na.rm = TRUE)

#Correlation
cor(gbr_sample$complexity, gbr_sample$flesh.grade, use = "complete.obs")

#T Test
t.test(gbr_sample$difference)

library(ggplot2)

ggplot(gbr_sample, aes(x = flesh.grade, y = complexity)) +
  geom_point(alpha = 0.4) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  labs(
    x = "Authors' Flesch Grade",
    y = "Replicated Flesch Grade",
    title = "Difference Between My Replication and Authors' Flesch-Kincaid Scores - GBR"
  ) +
  theme_minimal()

```
#Differences in Word Count and Sentence Count
💡 VERY IMPORTANT INSIGHT FOR YOUR PAPER
You are not just “recomputing” — you are testing:
👉 Is their reported complexity reproducible from raw text?
So your paper can say:
“We reconstruct word and sentence counts using independent tokenization methods”
“We compare reconstructed values to original dataset variables”
“Differences arise from preprocessing and tokenization choices”

Note: Fewer differences in English, GBR

```{r}
library(stringr)

gbr_sample$word_count <- str_count(gbr_sample$text, "\\S+")

gbr_sample$sentence_count <- str_count(gbr_sample$text, "[.!?]+")

# Differences
gbr_sample$diff_words <- gbr_sample$length - gbr_sample$word_count
gbr_sample$diff_sentences <- gbr_sample$sentences - gbr_sample$sentence_count

#correlations
cor(gbr_sample$length, gbr_sample$word_count)
cor(gbr_sample$sentences, gbr_sample$sentence_count)

# Graph
ggplot(gbr_sample, aes(x = length, y = word_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - GBR")

ggplot(gbr_sample, aes(x = sentences, y = sentence_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - GBR")

gbr_sample$country <- "UK"

saveRDS(gbr_sample, "gbr_sample_edited.rds")

```

# 2) ESP - Flesch Grade

```{r}
library(quanteda)
library(quanteda.textstats)

# create corpus
corp_esp <- corpus(esp_sample, text_field = "text")

# compute readability
readability_scores <- textstat_readability(
  corp_esp,
  measure = "Flesch.Kincaid"
)

# add score back to original data
esp_sample$complexity <- readability_scores$Flesch.Kincaid

head(readability_scores)
head(esp_sample$complexity)
summary(esp_sample$complexity)


# if your texts are in a data frame called df with column text
read_out <- textstat_readability(
  esp_sample$text,
  measure = "Flesch.Kincaid",
  intermediate = TRUE
)
names(read_out)
head(read_out)

# Extract Word, Word Count and Syllables - Quanteda
esp_sample$word_count_quanteda     <- read_out$W
esp_sample$sentence_count_quanteda <- read_out$St
esp_sample$syllables_quanteda      <- read_out$Sy

# Calculate Differences
esp_sample <- esp_sample %>%
  mutate(
    word_diff_q      = word_count_quanteda - length,
    sentence_diff_q  = sentence_count_quanteda - sentences,
    syllable_diff_q  = syllables_quanteda - syllables
  )

#Correlations 
cor(esp_sample$length, esp_sample$word_count_quanteda, use = "complete.obs")
cor(esp_sample$sentences, esp_sample$sentence_count_quanteda, use = "complete.obs")
cor(esp_sample$syllables, esp_sample$syllables_quanteda, use = "complete.obs")
```
```{r}
# Graph
ggplot(esp_sample, aes(x = length, y = word_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - ESP")

ggplot(esp_sample, aes(x = sentences, y = sentence_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - ESP")

ggplot(esp_sample, aes(x = syllables, y = syllables_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0)+
  labs(title = "Syllable Count: Original vs Replicated - ESP")

esp_sample$country <- "Spain"

saveRDS(esp_sample, "esp_sample_edited.rds")
```

# ESP - Assess Replication

7. How to explain this in your paper
You can confidently write:
“The Flesch-Kincaid scores are computed using the standard formula, identical to that implemented in common text analysis packages such as quanteda. Differences between the replicated and original scores are therefore attributable not to the formula itself, but to differences in text preprocessing, sentence segmentation, and syllable counting algorithms.”

✅ 1. Core result: VERY strong replication
The points lie tightly along the 45° line
Clear linear relationship across the entire range
👉 Interpretation:
✔ Your implementation is correct
✔ You are capturing the same underlying construct as the authors
⚠️ 2. But now we see a clearer pattern: systematic upward bias
Compared to your first plot, this one shows it much more clearly:
🔺 At higher values (≈ 25–40):
Your replicated scores are consistently ABOVE the red line
👉 Meaning:
You are systematically overestimating Flesch-Kincaid scores
And the bias increases with complexity
📈 3. This is NOT random error — it’s structural
This pattern is key:
Low scores → close to perfect
High scores → increasingly overestimated
👉 This tells us:
❌ Not noise
❌ Not random measurement error
✅ A systematic difference in how complexity is computed
🧠 4. What is causing this (very likely)?
Given the formula:
FK
=
0.39
⋅
words
sentences
+
11.8
⋅
syllables
words
−
15.59
FK=0.39⋅ 
sentences
words
​	
 +11.8⋅ 
words
syllables
​	
 −15.59
Your upward bias can only come from:
🔹 (A) Sentence splitting differences (MOST LIKELY)
If your code detects fewer sentences, then:
words
sentences
↑
sentences
words
​	
 ↑
→ FK score increases
→ especially for long/complex speeches
👉 This perfectly matches your pattern:
bias grows with complexity
🔹 (B) Syllable counting differences (SECOND LIKELY)
If quanteda:
slightly overcounts syllables, especially in Spanish
Then:
syllables
words
↑
words
syllables
​	
 ↑
→ FK score increases
🔹 (C) Language issue (VERY IMPORTANT HERE)
This is the Spanish dataset (ESP).
The authors note:
“languages may systematically differ in their complexity”
But more importantly:
👉 Flesch-Kincaid was designed for English
So:
Spanish syllable structure ≠ English
sentence punctuation rules differ
➡️ This amplifies discrepancies at higher complexity


```{r}
# Calculate Differences - My Complexity to Flesch Grade Score of Authors
esp_sample$difference <- esp_sample$complexity - esp_sample$flesh.grade
esp_sample$abs_diff <- abs(esp_sample$difference)

summary(esp_sample$difference)
mean(esp_sample$difference, na.rm = TRUE)
sd(esp_sample$difference, na.rm = TRUE)
mean(esp_sample$abs_diff, na.rm = TRUE)

#Correlation
cor(esp_sample$complexity, esp_sample$flesh.grade, use = "complete.obs")

#T Test
t.test(esp_sample$difference)

library(ggplot2)

ggplot(esp_sample, aes(x = flesh.grade, y = complexity)) +
  geom_point(alpha = 0.4) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  labs(
    x = "Authors' Flesch Grade",
    y = "Replicated Flesch Grade",
    title = "Difference Between My Replication and Authors' Flesch-Kincaid Scores - ESP"
  ) +
  theme_minimal()


```

```{r}
#Word Count and Sentences
esp_sample$word_count <- str_count(esp_sample$text, "\\S+")

esp_sample$sentence_count <- str_count(esp_sample$text, "[.!?]+")

# Differences
esp_sample$diff_words <- esp_sample$length - esp_sample$word_count
esp_sample$diff_sentences <- esp_sample$sentences - esp_sample$sentence_count

#correlations
cor(esp_sample$length, esp_sample$word_count)
cor(esp_sample$sentences, esp_sample$sentence_count)

# Graph
ggplot(esp_sample, aes(x = length, y = word_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - ESP")

ggplot(esp_sample, aes(x = sentences, y = sentence_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - ESP")


```

Differences in sentence count

## 3) GER - FLESCH GRADE

```{r}
# create corpus
corp_ger <- corpus(ger_sample, text_field = "text")

# compute readability
readability_scores <- textstat_readability(
  corp_ger,
  measure = "Flesch.Kincaid"
)

# add score back to original data
ger_sample$complexity <- readability_scores$Flesch.Kincaid

head(readability_scores)
head(ger_sample$complexity)
summary(ger_sample$complexity)

# if your texts are in a data frame called df with column text
read_out <- textstat_readability(
  ger_sample$text,
  measure = "Flesch.Kincaid",
  intermediate = TRUE
)
names(read_out)
head(read_out)

# Extract Word, Word Count and Syllables - Quanteda
ger_sample$word_count_quanteda     <- read_out$W
ger_sample$sentence_count_quanteda <- read_out$St
ger_sample$syllables_quanteda      <- read_out$Sy

# Calculate Differences
ger_sample <- ger_sample %>%
  mutate(
    word_diff_q      = word_count_quanteda - length,
    sentence_diff_q  = sentence_count_quanteda - sentences,
    syllable_diff_q  = syllables_quanteda - syllables
  )

#Correlations 
cor(ger_sample$length, ger_sample$word_count_quanteda, use = "complete.obs")
cor(ger_sample$sentences, ger_sample$sentence_count_quanteda, use = "complete.obs")
cor(ger_sample$syllables, ger_sample$syllables_quanteda, use = "complete.obs")

ger_sample$country <- "Germany"

saveRDS(ger_sample, "ger_sample_edited.rds")
```
```{r}
#graph 

ggplot(ger_sample, aes(x = length, y = word_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - GER")

ggplot(ger_sample, aes(x = sentences, y = sentence_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - GER")

ggplot(ger_sample, aes(x = syllables, y = syllables_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0)+
  labs(title = "Syllable Count: Original vs Replicated - GER")

ger_sample$country <- "Germany"

saveRDS(ger_sample, "ger_sample_edited.rds")
```


```{r}
# Calculate Differences - My Complexity to Flesch Grade Score of Authors
ger_sample$difference <- ger_sample$complexity - ger_sample$flesh.grade
ger_sample$abs_diff <- abs(ger_sample$difference)

summary(ger_sample$difference)
mean(ger_sample$difference, na.rm = TRUE)
sd(ger_sample$difference, na.rm = TRUE)
mean(ger_sample$abs_diff, na.rm = TRUE)

#Correlation
cor(ger_sample$complexity, ger_sample$flesh.grade, use = "complete.obs")

#T Test
t.test(ger_sample$difference)

library(ggplot2)

ggplot(ger_sample, aes(x = flesh.grade, y = complexity)) +
  geom_point(alpha = 0.4) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  labs(
    x = "Authors' Flesch Grade",
    y = "Replicated Flesch Grade",
    title = "Difference Between My Replication and Authors' Flesch-Kincaid Scores - GER"
  ) +
  theme_minimal()


```

```{r}
#Word Count and Sentences
ger_sample$word_count <- str_count(ger_sample$text, "\\S+")

ger_sample$sentence_count <- str_count(ger_sample$text, "[.!?]+")

# Differences
ger_sample$diff_words <- ger_sample$length - ger_sample$word_count
ger_sample$diff_sentences <- ger_sample$sentences - ger_sample$sentence_count

#correlations
cor(ger_sample$length, ger_sample$word_count)
cor(ger_sample$sentences, ger_sample$sentence_count)

# Graph
ggplot(ger_sample, aes(x = length, y = word_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - GER")

ggplot(ger_sample, aes(x = sentences, y = sentence_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - GER")

ger_sample$country <- "Germany"

saveRDS(ger_sample, "ger_sample_edited.rds")
```

## 4) NLD Parliament - Flesch Grade

Note: Flesh versus Flesch Grade

```{r}
# create corpus
corp_nld <- corpus(nld_sample, text_field = "text")

# compute readability
readability_scores <- textstat_readability(
  corp_nld,
  measure = "Flesch.Kincaid"
)

# add score back to original data
nld_sample$complexity <- readability_scores$Flesch.Kincaid

head(readability_scores)
head(nld_sample$complexity)
summary(nld_sample$complexity)


# if your texts are in a data frame called df with column text
read_out <- textstat_readability(
  nld_sample$text,
  measure = "Flesch.Kincaid",
  intermediate = TRUE
)
names(read_out)
head(read_out)

# Extract Word, Word Count and Syllables - Quanteda
nld_sample$word_count_quanteda     <- read_out$W
nld_sample$sentence_count_quanteda <- read_out$St
nld_sample$syllables_quanteda      <- read_out$Sy

# Calculate Differences
nld_sample <- nld_sample %>%
  mutate(
    word_diff_q      = word_count_quanteda - length,
    sentence_diff_q  = sentence_count_quanteda - sentences,
    syllable_diff_q  = syllables_quanteda - syllables
  )

#Correlations 
cor(nld_sample$length, nld_sample$word_count_quanteda, use = "complete.obs")
cor(nld_sample$sentences, nld_sample$sentence_count_quanteda, use = "complete.obs")
cor(nld_sample$syllables, nld_sample$syllables_quanteda, use = "complete.obs")


```
```{r}
#graph 

ggplot(nld_sample, aes(x = length, y = word_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - NLD")

ggplot(nld_sample, aes(x = sentences, y = sentence_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - NLD")

ggplot(nld_sample, aes(x = syllables, y = syllables_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0)+
  labs(title = "Syllable Count: Original vs Replicated - NLD")

nld_sample$country <- "Netherlands"

saveRDS(nld_sample, "nld_sample_edited.rds")
```

```{r}
# Calculate Differences - My Complexity to Flesch Grade Score of Authors
nld_sample$difference <- nld_sample$complexity - nld_sample$flesch.grade
nld_sample$abs_diff <- abs(nld_sample$difference)

summary(nld_sample$difference)
mean(nld_sample$difference, na.rm = TRUE)
sd(nld_sample$difference, na.rm = TRUE)
mean(nld_sample$abs_diff, na.rm = TRUE)

#Correlation
cor(nld_sample$complexity, nld_sample$flesch.grade, use = "complete.obs")

#T Test
t.test(nld_sample$difference)

library(ggplot2)

ggplot(nld_sample, aes(x = flesch.grade, y = complexity)) +
  geom_point(alpha = 0.4) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  labs(
    x = "Authors' Flesch Grade",
    y = "Replicated Flesch Grade",
    title = "Difference Between My Replication and Authors' Flesch-Kincaid Scores - NLD"
  ) +
  theme_minimal()


```


```{r}
#Word Count and Sentences
nld_sample$word_count <- str_count(nld_sample$text, "\\S+")

nld_sample$sentence_count <- str_count(nld_sample$text, "[.!?]+")

# Differences
nld_sample$diff_words <- nld_sample$length - nld_sample$word_count
nld_sample$diff_sentences <- nld_sample$sentences - nld_sample$sentence_count

#correlations
cor(nld_sample$length, nld_sample$word_count)
cor(nld_sample$sentences, nld_sample$sentence_count)

# Graph
ggplot(nld_sample, aes(x = length, y = word_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - NLD")

ggplot(nld_sample, aes(x = sentences, y = sentence_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - NLD")

nld_sample$country <- "Netherlands"

saveRDS(nld_sample, "nld_sample_edited.rds")
```

```{r}
# Combine 4 Data Sets

library(dplyr)

gbr_sample <- readRDS("gbr_sample_edited.rds")
esp_sample <- readRDS("esp_sample_edited.rds")
ger_sample <- readRDS("ger_sample_edited.rds")
nld_sample <- readRDS("nld_sample_edited.rds")

combined <- bind_rows(gbr_sample, esp_sample, ger_sample, nld_sample)

names(combined)

View(combined)      # spreadsheet view
head(combined)      # first rows
str(combined)       # structure (VERY important)
dim(combined)       # rows × columns

```
## 5) EU Parliament/Heads of Government - Flesch Grade - Replicate

1,790 observations

```{r}
library(quanteda)
library(quanteda.textstats)

# create corpus
corp_eu <- corpus(eu_sample, text_field = "text")

# compute readability
readability_scores <- textstat_readability(
  corp_eu,
  measure = "Flesch.Kincaid"
)

# add score back to original data
eu_sample$complexity <- readability_scores$Flesch.Kincaid

head(readability_scores)
head(eu_sample$complexity)
summary(eu_sample$complexity)

# if your texts are in a data frame called df with column text
read_out <- textstat_readability(
  eu_sample$text,
  measure = "Flesch.Kincaid",
  intermediate = TRUE
)
names(read_out)
head(read_out)

# Extract Word, Word Count and Syllables - Quanteda
eu_sample$word_count_quanteda     <- read_out$W
eu_sample$sentence_count_quanteda <- read_out$St
eu_sample$syllables_quanteda      <- read_out$Sy

# Calculate Differences
eu_sample <- eu_sample %>%
  mutate(
    word_diff_q      = word_count_quanteda - length,
    sentence_diff_q  = sentence_count_quanteda - sentences,
    syllable_diff_q  = syllables_quanteda - syllables
  )

#Correlations 
cor(eu_sample$length, eu_sample$word_count_quanteda, use = "complete.obs")
cor(eu_sample$sentences, eu_sample$sentence_count_quanteda, use = "complete.obs")
cor(eu_sample$syllables, eu_sample$syllables_quanteda, use = "complete.obs")

```
```{r}
#graph 

ggplot(eu_sample, aes(x = length, y = word_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - EU")

ggplot(eu_sample, aes(x = sentences, y = sentence_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - EU")

ggplot(eu_sample, aes(x = syllables, y = syllables_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0)+
  labs(title = "Syllable Count: Original vs Replicated - EU")

saveRDS(eu_sample, "eu_sample_edited.rds")
```


```{r}
# Calculate Differences - My Complexity to Flesch Grade Score of Authors
eu_sample$difference <- eu_sample$complexity - eu_sample$flesh.grade
eu_sample$abs_diff <- abs(eu_sample$difference)

summary(eu_sample$difference)
mean(eu_sample$difference, na.rm = TRUE)
sd(eu_sample$difference, na.rm = TRUE)
mean(eu_sample$abs_diff, na.rm = TRUE)

#Correlation
cor(eu_sample$complexity, eu_sample$flesh.grade, use = "complete.obs")

#T Test
t.test(eu_sample$difference)

library(ggplot2)

ggplot(eu_sample, aes(x = flesh.grade, y = complexity)) +
  geom_point(alpha = 0.4) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  labs(
    x = "Authors' Flesch Grade",
    y = "Replicated Flesch Grade",
    title = "Difference Between My Replication and Authors' Flesch-Kincaid Scores - EU"
  ) +
  theme_minimal()

```

```{r}
#Word Count and Sentences
eu_sample$word_count <- str_count(eu_sample$text, "\\S+")

eu_sample$sentence_count <- str_count(eu_sample$text, "[.!?]+")

# Differences
eu_sample$diff_words <- eu_sample$length - eu_sample$word_count
eu_sample$diff_sentences <- eu_sample$sentences - eu_sample$sentence_count

#correlations
cor(eu_sample$length, eu_sample$word_count)
cor(eu_sample$sentences, eu_sample$sentence_count)

# Graph
ggplot(eu_sample, aes(x = length, y = word_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - EU")

ggplot(eu_sample, aes(x = sentences, y = sentence_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - EU")

saveRDS(eu_sample, "eu_sample_edited.rds")
```
## 6) CONGRESS NETHERLANDS - Flesch Grade - Replicate

673 observations


```{r}
library(quanteda)
library(quanteda.textstats)

# create corpus
corp_cong_nld <- corpus(congress_nld_sample, text_field = "text")

# compute readability
readability_scores <- textstat_readability(
  corp_cong_nld,
  measure = "Flesch.Kincaid"
)

# add score back to original data
congress_nld_sample$complexity <- readability_scores$Flesch.Kincaid

head(readability_scores)
head(congress_nld_sample$complexity)
summary(congress_nld_sample$complexity)

# if your texts are in a data frame called df with column text
read_out <- textstat_readability(
  congress_nld_sample$text,
  measure = "Flesch.Kincaid",
  intermediate = TRUE
)
names(read_out)
head(read_out)

# Extract Word, Word Count and Syllables - Quanteda
congress_nld_sample$word_count_quanteda     <- read_out$W
congress_nld_sample$sentence_count_quanteda <- read_out$St
congress_nld_sample$syllables_quanteda      <- read_out$Sy

# Calculate Differences
congress_nld_sample <- congress_nld_sample %>%
  mutate(
    word_diff_q      = word_count_quanteda - length,
    sentence_diff_q  = sentence_count_quanteda - sentences,
    syllable_diff_q  = syllables_quanteda - syllables
  )

#Correlations 
cor(congress_nld_sample$length, congress_nld_sample$word_count_quanteda, use = "complete.obs")
cor(congress_nld_sample$sentences, congress_nld_sample$sentence_count_quanteda, use = "complete.obs")
cor(congress_nld_sample$syllables, congress_nld_sample$syllables_quanteda, use = "complete.obs")
```
```{r}
#graph 

ggplot(congress_nld_sample, aes(x = length, y = word_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - Congress NLD")

ggplot(congress_nld_sample, aes(x = sentences, y = sentence_count_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - Congress NLD")

ggplot(congress_nld_sample, aes(x = syllables, y = syllables_quanteda)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0)+
  labs(title = "Syllable Count: Original vs Replicated - Congress NLD")

saveRDS(congress_nld_sample, "congress_nld_sample_edited.rds")
```


```{r}
# Calculate Differences - My Complexity to Flesch Grade Score of Authors
congress_nld_sample$difference <- congress_nld_sample$complexity - congress_nld_sample$flesh.grade
congress_nld_sample$abs_diff <- abs(congress_nld_sample$difference)

summary(congress_nld_sample$difference)
mean(congress_nld_sample$difference, na.rm = TRUE)
sd(congress_nld_sample$difference, na.rm = TRUE)
mean(congress_nld_sample$abs_diff, na.rm = TRUE)

#Correlation
cor(congress_nld_sample$complexity, congress_nld_sample$flesh.grade, use = "complete.obs")

#T Test
t.test(congress_nld_sample$difference)

library(ggplot2)

ggplot(congress_nld_sample, aes(x = flesh.grade, y = complexity)) +
  geom_point(alpha = 0.4) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  labs(
    x = "Authors' Flesch Grade",
    y = "Replicated Flesch Grade",
    title = "Difference Between My Replication and Authors' Flesch-Kincaid Scores - Congress NLD"
  ) +
  theme_minimal()
```

```{r}
#Word Count and Sentences
congress_nld_sample$word_count <- str_count(congress_nld_sample$text, "\\S+")

congress_nld_sample$sentence_count <- str_count(congress_nld_sample$text, "[.!?]+")

# Differences
congress_nld_sample$diff_words <- congress_nld_sample$length - congress_nld_sample$word_count
congress_nld_sample$diff_sentences <- congress_nld_sample$sentences - congress_nld_sample$sentence_count

#correlations
cor(congress_nld_sample$length, congress_nld_sample$word_count)
cor(congress_nld_sample$sentences, congress_nld_sample$sentence_count)

# Graph
ggplot(congress_nld_sample, aes(x = length, y = word_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Word Count: Original vs Replicated - CONGRESS NLD")

ggplot(congress_nld_sample, aes(x = sentences, y = sentence_count)) +
  geom_point(alpha = 0.3) +
  geom_abline(slope = 1, intercept = 0) +
  labs(title = "Sentence Count: Original vs Replicated - CONGRESS NLD")

saveRDS(congress_nld_sample, "congress_nld_sample_edited.rds")
```
# Create Combined Other data set (EU and Congress NLD)
2,463 observations

```{r}

# Combine 2 other Data Sets

library(dplyr)

eu_sample <- readRDS("eu_sample_edited.rds")
congress_nld_sample <- readRDS("congress_nld_sample_edited.rds")

combined_other <- bind_rows(eu_sample, congress_nld_sample)

names(combined_other)
View(combined_other)

```

## REPLICATE FIGURES AND GRAPHS USING COMBINED (PARLIAMENT)

#Main Regression Code
```{r}

# Create mean centered year
combined$year2 <- combined$year - mean(combined$year, na.rm = TRUE)

vars1 <- as.formula(scale(complexity) ~ scale(lr) + scale(pc) + year2 + cabinet.party) #change from office to cabinet.party

reg.output <- list()
reg.output[[1]] <- lm(vars1, data = combined,
                      subset = country == "Germany")
reg.output[[2]] <- lm(vars1, data = combined,
                      subset = country == "Spain")
reg.output[[3]] <- lm(vars1, data = combined,
                      subset = country == "UK")
reg.output[[4]] <- lm(vars1, data = combined,
                      subset = country == "Netherlands")
```

# Figure 2a

```{r}

coefs <- unlist(lapply(reg.output, function(x) coef(x)[3]))
se    <- unlist(lapply(reg.output, function(x) sqrt(diag(vcov(x)))[3]))
min   <- coefs - 1.96 * se
max   <- coefs + 1.96 * se

names_vec <- c("Parliament GER", "Parliament ESP", "Parliament GBR", "Parliament NLD")

plot.data <- data.frame(
  names = names_vec,
  coefs = coefs,
  se = se,
  min = min,
  max = max
)

plot.data$names <- factor(plot.data$names, levels = rev(plot.data$names))

coef.plot2a <- ggplot(plot.data, aes(x = names, y = coefs)) +
  geom_point(size = 1) +
  geom_errorbar(aes(ymin = min, ymax = max), width = .1) +
  coord_flip() +
  ylab("Effect of lib-cons ideology") +
  xlab("") +
  geom_hline(yintercept = 0) +
  theme_minimal()

print(coef.plot2a)
```

# Figure 2b

```{r}
coefs <- unlist(lapply(reg.output, function(x) coef(x)[2]))
se    <- unlist(lapply(reg.output, function(x) sqrt(diag(vcov(x)))[2]))
min   <- coefs - 1.96 * se
max   <- coefs + 1.96 * se

names_vec <- c("Parliament GER", "Parliament ESP", "Parliament GBR", "Parliament NLD")

plot.data <- data.frame(
  names = names_vec,
  coefs = coefs,
  se = se,
  min = min,
  max = max
)

plot.data$names <- factor(plot.data$names, levels = rev(plot.data$names))

coef.plot2b <- ggplot(plot.data, aes(x = names, y = coefs)) +
  geom_point(size = 1) +
  geom_errorbar(aes(ymin = min, ymax = max), width = .1) +
  coord_flip() +
  ylab("Effect of left-right ideology") +
  xlab("") +
  geom_hline(yintercept = 0) +
  theme_minimal()

print(coef.plot2b)
```

## Government/Opposition Plot

```{r}
coefs <- unlist(lapply(reg.output, function(x) coef(x)[5]))
se    <- unlist(lapply(reg.output, function(x) sqrt(diag(vcov(x)))[5]))
min   <- coefs - 1.96 * se
max   <- coefs + 1.96 * se

names_vec <- c("Parliament GER", "Parliament ESP", "Parliament GBR", "Parliament NLD")

plot.data <- data.frame(
  names = names_vec,
  coefs = coefs,
  se = se,
  min = min,
  max = max
)

plot.data$names <- factor(plot.data$names, levels = rev(plot.data$names))

coef.plotb1 <- ggplot(plot.data, aes(x = names, y = coefs)) +
  geom_point(size = 1) +
  geom_errorbar(aes(ymin = min, ymax = max), width = .1) +
  coord_flip() +
  ylab("Effect of government status") +
  xlab("") +
  geom_hline(yintercept = 0) +
  theme_minimal()

print(coef.plotb1)
```

## Figure 3A) Time Series Plot

```{r}
combined.subset <- combined

combined.subset$id <- ifelse(combined.subset$country == "Germany", "GER",
                      ifelse(combined.subset$country == "Spain", "ESP",
                      ifelse(combined.subset$country == "UK", "GBR",
                      ifelse(combined.subset$country == "Netherlands", "NLD", NA))))

combined.subset$year <- as.numeric(combined.subset$year)

time.plot.parl <- ggplot(combined.subset, aes(x = year, y = complexity)) +
  geom_smooth(se = FALSE) +
  facet_wrap(~id, nrow = 1) +
  scale_x_continuous(breaks = c(1990, 2000, 2010), labels = c("'90", "'00", "'10")) +
  ylab("Complexity") +
  xlab("") +
  theme_minimal()

print(time.plot.parl)
```
## Figure 4a) Fixed Effects Model

```{r}
vars3 <- as.formula(complexity ~ lr + pc + year2 + cabinet.party + factor(speaker))

reg.output.fixed <- list()
reg.output.fixed[[1]] <- lm(vars3, data = combined,
                            subset = country == "Germany")
reg.output.fixed[[2]] <- lm(vars3, data = combined,
                            subset = country == "Spain")
reg.output.fixed[[3]] <- lm(vars3, data = combined,
                            subset = country == "UK")
reg.output.fixed[[4]] <- lm(vars3, data = combined,
                            subset = country == "Netherlands")

coefs <- unlist(lapply(reg.output.fixed, function(x) coef(x)[3]))
se    <- unlist(lapply(reg.output.fixed, function(x) sqrt(diag(vcov(x)))[3]))
min   <- coefs - 1.96 * se
max   <- coefs + 1.96 * se

names_vec <- c("Parliament GER", "Parliament ESP", "Parliament GBR", "Parliament NLD")

plot.data <- data.frame(
  names = names_vec,
  coefs = coefs,
  se = se,
  min = min,
  max = max
)

plot.data$names <- factor(plot.data$names, levels = rev(plot.data$names))

coef.plot3 <- ggplot(plot.data, aes(x = names, y = coefs)) +
  geom_point() +
  geom_errorbar(aes(ymin = min, ymax = max), width = .1) +
  coord_flip() +
  ylab("Fixed effect of conservatism") +
  xlab("") +
  geom_hline(yintercept = 0) +
  theme_minimal()

print(coef.plot3)
```

# Figure 1

```{r}
library(plyr)
library(dplyr)

view(combined)
```


```{r}
# Checking Speaker Names
unique(combined$speaker)

combined_all <-combined

table(combined_all[combined_all$speaker %in% c(
  "David Cameron","Gordon Brown","rodriguez zapatero","rajoy brey"
), "speaker"])

table(combined_all[combined_all$speaker %in% c(
  "Joseph Fischer","Nick Clegg","Wilders"
), "speaker"])

#Sara had to fix. Check names of candidates in dataset rather than official name

#missing example1 - Sara had to add
combined1 <-  combined_all[combined_all$speaker%in%c("David Cameron","Gordon Brown","rodriguez zapatero","rajoy brey"),]
example1 <- ddply(combined1, "speaker", summarise, 
                 mean=mean(complexity, na.rm=TRUE), 
                 SD=sd(complexity, na.rm=TRUE), #change to complexity(replication)
                 N=length(speaker)) #fix
example1$N=as.numeric(example1$N)
example1$se <- example1$SD / sqrt(example1$N)
example1$min <- example1$mean - 1.96*example1$se
example1$max <- example1$mean + 1.96*example1$se

#example 2
combined2 <-combined_all[combined_all$speaker%in%c("Joseph Fischer","Nick Clegg","Wilders"),]
example2 <- ddply(combined2, "speaker", summarise, 
                 mean=mean(complexity, na.rm=TRUE), 
                 SD=sd(complexity, na.rm=TRUE), #change to complexity (replication)
                 N=length(speaker)) #fix
example2$N=as.numeric(example2$N)
example2$se <- example2$SD / sqrt(example2$N)
example2$min <- example2$mean - 1.96*example2$se
example2$max <- example2$mean + 1.96*example2$se


example <- rbind(example1,example2)
example$speaker <- c("Brown", "Cameron", "zapatero", "rajoy", "Fischer", "Clegg", "Wilders")
example$prog <- c(1,0,1,0,1,1,0)
order <- c(1,2,3,4,5,6,7)
example <- example[order,]
example$speaker <- factor(example$speaker, levels=example$speaker)
example$country <- c("gb","gb","es", "es", "ger", "gb", "nl")
example$label <- c("UK","UK","ES","ES","GER","UK","NL")



desc.plot <- ggplot(example, aes(x=speaker, y=mean, fill=factor(prog), country=country)) + 
  geom_bar(stat="identity") + 
  geom_errorbar(ymin=example$min,ymax=example$max, width=.2) + 
geom_text(aes(y = max + 0.5, label = country),
          hjust = -0.2,
          size = 4)+
  coord_flip() + 
  xlab("") +
  ylab("Mean Complexity") + 
  scale_fill_manual(values=c("#56B4E9","#E69F00")) + #"#999999"
  theme_minimal() + 
  ylim(c(0,30)) + 
  guides(fill=FALSE)


ggsave(
  filename = "fig1.pdf",
  plot = desc.plot,
  dpi = 900
)

print(desc.plot)
```

## APPENDICES

```{r}
# =========================================================
# APPENDIX REPLICATION SCRIPT
# Export tables as PNG/PDF using gt + webshot2
# Export figure as PNG/PDF using ggplot2::ggsave
# Countries: Great Britain, Netherlands, Germany, Spain
# =========================================================

rm(list = ls())

# -----------------------------
# 1. PACKAGES
# -----------------------------
# install.packages(c("dplyr", "ggplot2", "broom", "gt", "webshot2"))

library(dplyr)
library(ggplot2)
library(broom)
library(gt)
library(webshot2)
install.packages("xfun")
install.packages(c("knitr", "rmarkdown", "gt", "htmltools", "webshot2"))
library(xfun)

# -----------------------------
# 2. DATA
# -----------------------------
# Assumes your combined dataset is already loaded as: combined
gbr_sample <- readRDS("gbr_sample_edited.rds")
esp_sample <- readRDS("esp_sample_edited.rds")
ger_sample <- readRDS("ger_sample_edited.rds")
nld_sample <- readRDS("nld_sample_edited.rds")

combined <- bind_rows(gbr_sample, esp_sample, ger_sample, nld_sample)

View(combined)

# -----------------------------
# 3. STANDARDIZE COUNTRY LABELS
# -----------------------------
combined <- combined %>%
  mutate(
    country = case_when(
      country %in% c("UK", "GBR", "Great Britain", "Britain", "United Kingdom") ~ "GBR",
      country %in% c("Netherlands", "NLD", "NL") ~ "NLD",
      country %in% c("Germany", "GER", "DE") ~ "GER",
      country %in% c("Spain", "ESP", "ES") ~ "ESP",
      TRUE ~ as.character(country)
    )
  )

combined4 <- combined %>%
  filter(country %in% c("GBR", "NLD", "GER", "ESP"))

# -----------------------------
# 4. CREATE GOVERNMENT VARIABLE
# -----------------------------
if ("cabinet.party" %in% names(combined4)) {
  combined4 <- combined4 %>%
    mutate(in_government = cabinet.party)
} else if ("office" %in% names(combined4)) {
  combined4 <- combined4 %>%
    mutate(in_government = office)
} else {
  stop("Need a government-status variable: neither `cabinet.party` nor `office` exists.")
}

combined4 <- combined4 %>%
  mutate(
    in_government = case_when(
      in_government %in% c(TRUE, "TRUE", "True", "yes", "Yes", "Y", "1") ~ 1,
      in_government %in% c(FALSE, "FALSE", "False", "no", "No", "N", "0") ~ 0,
      TRUE ~ suppressWarnings(as.numeric(as.character(in_government)))
    )
  )

# -----------------------------
# 5. CREATE RELATIVE YEAR
# -----------------------------
# The appendix tables show year starting at 0 within corpus. :contentReference[oaicite:1]{index=1}

combined4 <- combined4 %>%
  group_by(country) %>%
  mutate(year_rel = year - min(year, na.rm = TRUE)) %>%
  ungroup()

# -----------------------------
# 6. OPTIONAL FILTER
# -----------------------------
# Uncomment if needed:
# combined4 <- combined4 %>%
#   filter(data.set == "parliamentary speeches")

table(combined4$country, useNA = "ifany")

# =========================================================
# 7. HELPER FUNCTIONS
# =========================================================

# Save a gt table to both PNG and PDF using HTML + webshot2
save_gt_dual <- function(gt_obj, base_name, zoom = 2.5) {
  html_file <- paste0(base_name, ".html")
  png_file  <- paste0(base_name, ".png")
  pdf_file  <- paste0(base_name, ".pdf")

  gtsave(gt_obj, filename = html_file)

  webshot2::webshot(
    url = html_file,
    file = png_file,
    zoom = zoom
  )

  webshot2::webshot(
    url = html_file,
    file = pdf_file,
    zoom = zoom
  )
}

# Nice gt theme
style_gt <- function(gt_obj) {
  gt_obj %>%
    tab_options(
      table.font.size = px(13),
      heading.title.font.size = px(16),
      heading.subtitle.font.size = px(12),
      data_row.padding = px(4),
      table.width = pct(100)
    ) %>%
    opt_table_outline() %>%
    opt_row_striping() %>%
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels(everything())
    )
}

# Format p-values as stars
star_p <- function(p) {
  case_when(
    is.na(p)      ~ "",
    p < 0.01      ~ "***",
    p < 0.05      ~ "**",
    p < 0.10      ~ "*",
    TRUE          ~ ""
  )
}

# Build regression table like appendix layout:
# estimate on one line, SE in parentheses on next line
make_reg_table <- function(model_list, col_labels, table_title, note_text,
                           add_party_fe = FALSE) {

  term_order <- c("(Intercept)", "lr", "pc", "year_rel", "in_government")
  term_labels <- c(
    "(Intercept)"   = "Constant",
    "lr"            = "Left-Right",
    "pc"            = "Progressive-Conservative",
    "year_rel"      = "Year",
    "in_government" = "In government"
  )

  coef_blocks <- lapply(seq_along(model_list), function(i) {
    td <- broom::tidy(model_list[[i]]) %>%
      filter(term %in% term_order) %>%
      mutate(
        estimate_fmt = sprintf("%.3f%s", estimate, star_p(p.value)),
        se_fmt = sprintf("(%.3f)", std.error)
      ) %>%
      select(term, estimate_fmt, se_fmt)

    full_terms <- tibble(term = term_order) %>%
      left_join(td, by = "term") %>%
      mutate(
        estimate_fmt = ifelse(is.na(estimate_fmt), "", estimate_fmt),
        se_fmt = ifelse(is.na(se_fmt), "", se_fmt)
      )

    out <- tibble(
      row_key = c(rbind(term_order, paste0(term_order, "_se"))),
      !!col_labels[i] := c(rbind(full_terms$estimate_fmt, full_terms$se_fmt))
    )

    out
  })

  coef_table <- Reduce(function(x, y) full_join(x, y, by = "row_key"), coef_blocks)

  label_df <- tibble(
    row_key = c(rbind(term_order, paste0(term_order, "_se"))),
    term_label = c(rbind(unname(term_labels[term_order]), rep("", length(term_order))))
  )

  body <- label_df %>%
    left_join(coef_table, by = "row_key") %>%
    select(term_label, all_of(col_labels))

  # GOF rows
  gof_rows <- tibble(
    term_label = c("Observations", "R2", "Adjusted R2", "Residual Std. Error", "F Statistic"),
    !!!setNames(vector("list", length(col_labels)), col_labels)
  )

  for (i in seq_along(model_list)) {
    sm <- summary(model_list[[i]])
    fstat <- sm$fstatistic

    gof_rows[[col_labels[i]]] <- c(
      format(nobs(model_list[[i]]), big.mark = ","),
      sprintf("%.3f", sm$r.squared),
      sprintf("%.3f", sm$adj.r.squared),
      sprintf("%.3f", sm$sigma),
      sprintf("%.3f", unname(fstat[1]))
    )
  }

  if (add_party_fe) {
    fe_row <- tibble(
      term_label = "Party Fixed Effects?",
      !!!setNames(as.list(rep("Yes", length(col_labels))), col_labels)
    )
    final_table <- bind_rows(body, fe_row, gof_rows)
  } else {
    final_table <- bind_rows(body, gof_rows)
  }

  gt_tbl <- final_table %>%
    gt(rowname_col = "term_label") %>%
    tab_header(
      title = md(table_title)
    ) %>%
    cols_label(.list = setNames(as.list(col_labels), col_labels)) %>%
    cols_align(
      align = "center",
      columns = all_of(col_labels)
    ) %>%
    tab_source_note(
      source_note = note_text
    ) %>%
    style_gt()

  gt_tbl
}

# =========================================================
# APPENDIX A: DESCRIPTIVE TABLES
# Tables A.3, A.4, A.5, A.7 in your four-country setup. :contentReference[oaicite:2]{index=2}
# =========================================================

make_desc_table <- function(df, country_code) {
  sub <- df %>% filter(country == country_code)

  tibble(
    Statistic = c("Complexity", "Left-Right", "Progressive-Conservative", "Year", "In government"),
    N = c(
      sum(!is.na(sub$complexity)),
      sum(!is.na(sub$lr)),
      sum(!is.na(sub$pc)),
      sum(!is.na(sub$year_rel)),
      sum(!is.na(sub$in_government))
    ),
    Mean = c(
      mean(sub$complexity, na.rm = TRUE),
      mean(sub$lr, na.rm = TRUE),
      mean(sub$pc, na.rm = TRUE),
      mean(sub$year_rel, na.rm = TRUE),
      mean(sub$in_government, na.rm = TRUE)
    ),
    `St. Dev.` = c(
      sd(sub$complexity, na.rm = TRUE),
      sd(sub$lr, na.rm = TRUE),
      sd(sub$pc, na.rm = TRUE),
      sd(sub$year_rel, na.rm = TRUE),
      sd(sub$in_government, na.rm = TRUE)
    ),
    Min = c(
      min(sub$complexity, na.rm = TRUE),
      min(sub$lr, na.rm = TRUE),
      min(sub$pc, na.rm = TRUE),
      min(sub$year_rel, na.rm = TRUE),
      min(sub$in_government, na.rm = TRUE)
    ),
    `Pctl(25)` = c(
      quantile(sub$complexity, 0.25, na.rm = TRUE),
      quantile(sub$lr, 0.25, na.rm = TRUE),
      quantile(sub$pc, 0.25, na.rm = TRUE),
      quantile(sub$year_rel, 0.25, na.rm = TRUE),
      quantile(sub$in_government, 0.25, na.rm = TRUE)
    ),
    `Pctl(75)` = c(
      quantile(sub$complexity, 0.75, na.rm = TRUE),
      quantile(sub$lr, 0.75, na.rm = TRUE),
      quantile(sub$pc, 0.75, na.rm = TRUE),
      quantile(sub$year_rel, 0.75, na.rm = TRUE),
      quantile(sub$in_government, 0.75, na.rm = TRUE)
    ),
    Max = c(
      max(sub$complexity, na.rm = TRUE),
      max(sub$lr, na.rm = TRUE),
      max(sub$pc, na.rm = TRUE),
      max(sub$year_rel, na.rm = TRUE),
      max(sub$in_government, na.rm = TRUE)
    )
  ) %>%
    mutate(
      N = format(N, big.mark = ","),
      across(c(Mean, `St. Dev.`, Min, `Pctl(25)`, `Pctl(75)`, Max), ~ round(., 3))
    )
}

table_A3_GER <- make_desc_table(combined4, "GER")
table_A4_ESP <- make_desc_table(combined4, "ESP")
table_A5_GBR <- make_desc_table(combined4, "GBR")
table_A7_NLD <- make_desc_table(combined4, "NLD")

gt_A3 <- table_A3_GER %>%
  gt(rowname_col = "Statistic") %>%
  tab_header(title = md("**Table A.3: Parliament GER**")) %>%
  style_gt()

gt_A4 <- table_A4_ESP %>%
  gt(rowname_col = "Statistic") %>%
  tab_header(title = md("**Table A.4: Parliament ESP**")) %>%
  style_gt()

gt_A5 <- table_A5_GBR %>%
  gt(rowname_col = "Statistic") %>%
  tab_header(title = md("**Table A.5: Parliament GBR**")) %>%
  style_gt()

gt_A7 <- table_A7_NLD %>%
  gt(rowname_col = "Statistic") %>%
  tab_header(title = md("**Table A.7: Parliament NLD**")) %>%
  style_gt()

gtsave(gt_A3, "Table_A3_Parliament_GER.html")
gtsave(gt_A4, "Table_A4_Parliament_ESP.html")
gtsave(gt_A5, "Table_A5_Parliament_GBR.html")
gtsave(gt_A7, "Table_A7_Parliament_NLD.html")

# Optional combined Appendix A file
appendix_A_all <- bind_rows(
  table_A3_GER %>% mutate(Corpus = "Parliament GER"),
  table_A4_ESP %>% mutate(Corpus = "Parliament ESP"),
  table_A5_GBR %>% mutate(Corpus = "Parliament GBR"),
  table_A7_NLD %>% mutate(Corpus = "Parliament NLD")
) %>%
  select(Corpus, everything())

gt_A_all <- appendix_A_all %>%
  gt(groupname_col = "Corpus", rowname_col = "Statistic") %>%
  tab_header(title = md("**Appendix A: Descriptive statistics**")) %>%
  style_gt()

gtsave(gt_A_all, "Appendix_A_all_descriptives.html")

# =========================================================
# APPENDIX B: FIGURE B.1
# OLS regression of complexity on government status and time. :contentReference[oaicite:3]{index=3}
# =========================================================

model_B_GER <- lm(scale(complexity) ~ scale(lr) + scale(pc) + year_rel + in_government,
                  data = combined4, subset = country == "GER")

model_B_ESP <- lm(scale(complexity) ~ scale(lr) + scale(pc) + year_rel + in_government,
                  data = combined4, subset = country == "ESP")

model_B_GBR <- lm(scale(complexity) ~ scale(lr) + scale(pc) + year_rel + in_government,
                  data = combined4, subset = country == "GBR")

model_B_NLD <- lm(scale(complexity) ~ scale(lr) + scale(pc) + year_rel + in_government,
                  data = combined4, subset = country == "NLD")

coef_B <- bind_rows(
  tidy(model_B_NLD, conf.int = TRUE) %>% mutate(dataset = "Parliament NLD"),
  tidy(model_B_GBR, conf.int = TRUE) %>% mutate(dataset = "Parliament GBR"),
  tidy(model_B_ESP, conf.int = TRUE) %>% mutate(dataset = "Parliament ESP"),
  tidy(model_B_GER, conf.int = TRUE) %>% mutate(dataset = "Parliament GER")
) %>%
  filter(term == "in_government")

coef_B$dataset <- factor(
  coef_B$dataset,
  levels = c("Parliament NLD", "Parliament GBR", "Parliament ESP", "Parliament GER")
)

fig_B1 <- ggplot(coef_B, aes(x = estimate, y = dataset)) +
  geom_point(size = 2.8) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.15) +
  geom_vline(xintercept = 0, linetype = "solid") +
  labs(
    title = "Figure B.1: OLS regression of complexity on government status and time",
    subtitle = "Government status and complexity",
    x = "Effect of government status",
    y = NULL,
    caption = "Note: This plot reports standardized regression coefficients for government-opposition status in four OLS regression models. The bars represent the 95% confidence intervals of the coefficients."
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(face = "bold"),
    axis.text.y = element_text(size = 11),
    plot.caption = element_text(size = 9, hjust = 0)
  )

ggsave("Figure_B1_government_status.png", fig_B1, width = 8.5, height = 5.5, dpi = 300)
ggsave("Figure_B1_government_status.pdf", fig_B1, width = 8.5, height = 5.5)

# =========================================================
# APPENDIX C: TABLE C.1 OLS REGRESSION RESULTS
# complexity ~ lr + pc + year + in government. :contentReference[oaicite:4]{index=4}
# =========================================================

model_C_GER <- lm(complexity ~ lr + pc + year_rel + in_government,
                  data = combined4, subset = country == "GER")

model_C_ESP <- lm(complexity ~ lr + pc + year_rel + in_government,
                  data = combined4, subset = country == "ESP")

model_C_GBR <- lm(complexity ~ lr + pc + year_rel + in_government,
                  data = combined4, subset = country == "GBR")

model_C_NLD <- lm(complexity ~ lr + pc + year_rel + in_government,
                  data = combined4, subset = country == "NLD")

gt_C1 <- make_reg_table(
  model_list = list(model_C_GER, model_C_ESP, model_C_GBR, model_C_NLD),
  col_labels = c("GER Parl", "ESP Parl", "GBR Parl", "NLD Parl"),
  table_title = "**Table C.1: OLS regression results**",
  note_text = md("Note: *p*<0.1; **p*<0.05; ***p*<0.01")
)

gtsave(gt_C1, "Table_C1_OLS.html")


# =========================================================
# APPENDIX D: TABLE D.1 SPEAKER FIXED EFFECTS
# Speaker fixed effects regression models of complexity. :contentReference[oaicite:5]{index=5}
# =========================================================

model_D_GER <- lm(complexity ~ lr + pc + year_rel + in_government + factor(speaker),
                  data = combined4, subset = country == "GER")

model_D_ESP <- lm(complexity ~ lr + pc + year_rel + in_government + factor(speaker),
                  data = combined4, subset = country == "ESP")

model_D_GBR <- lm(complexity ~ lr + pc + year_rel + in_government + factor(speaker),
                  data = combined4, subset = country == "GBR")

model_D_NLD <- lm(complexity ~ lr + pc + year_rel + in_government + factor(speaker), data = combined4, subset = country == "NLD")

gt_D1 <- make_reg_table(
  model_list = list(model_D_GER, model_D_ESP, model_D_GBR, model_D_NLD),
  col_labels = c("GER Parl", "ESP Parl", "GBR Parl", "NLD Parl"),
  table_title = "**Table D.1: Speaker fixed effects regression results**",
  note_text = md("Note: *p*<0.1; **p*<0.05; ***p*<0.01"),
  add_party_fe = TRUE
)

gtsave(gt_D1, "Table_D1_Speaker_FE.html")


# =========================================================
# 8. DIAGNOSTICS
# =========================================================

cat("\nFiles saved to:\n")
print(getwd())

cat("\nCreated files:\n")
print(list.files(pattern = "Table_|Appendix_A|Figure_B1"))

cat("\nObservations used in OLS models:\n")
print(c(
  GER = nobs(model_C_GER),
  ESP = nobs(model_C_ESP),
  GBR = nobs(model_C_GBR),
  NLD = nobs(model_C_NLD)
))

cat("\nObservations used in FE models:\n")
print(c(
  GER = nobs(model_D_GER),
  ESP = nobs(model_D_ESP),
  GBR = nobs(model_D_GBR),
  NLD = nobs(model_D_NLD)
))

```

## REPLICATION MAIN FIGURES AND TABLES - COMBINED OTHER (EU AND CONGRESS NLD)

# FIGURE 2A 

```{r}
# ---------------------------------
# FIGURE 2A USING combined_other
# ---------------------------------

library(ggplot2)

eu_sample <- readRDS("eu_sample_edited.rds")
congress_nld_sample <- readRDS("congress_nld_sample_edited.rds")

combined_other <- bind_rows(eu_sample, congress_nld_sample)

names(combined_other)
View(combined_other)

# Create mean-centered year
combined_other$year2 <- combined_other$year - mean(combined_other$year, na.rm = TRUE)

# Main regression formula
vars1 <- as.formula(scale(complexity) ~ scale(lr) + scale(pc) + year2)

# Run models for the datasets in combined_other
reg.output.other <- list()

# 1. EU / Heads of Government
reg.output.other[[1]] <- lm(
  vars1,
  data = combined_other,
  subset = parliament == "Heads of Government"
)

# 2. Netherlands Congress
reg.output.other[[2]] <- lm(
  vars1,
  data = combined_other,
  subset = parliament == "Dutch Congress Speeches"
)

# Extract coefficient on pc (the 3rd coefficient in your model)
coefs <- unlist(lapply(reg.output.other, function(x) coef(x)[3]))
se    <- unlist(lapply(reg.output.other, function(x) sqrt(diag(vcov(x)))[3]))
min   <- coefs - 1.96 * se
max   <- coefs + 1.96 * se

# Labels for plot
names_vec <- c("Heads of Government", "Congress NLD")

plot.data <- data.frame(
  names = names_vec,
  coefs = coefs,
  se = se,
  min = min,
  max = max
)

plot.data$names <- factor(plot.data$names, levels = rev(plot.data$names))

coef.plot2a_other <- ggplot(plot.data, aes(x = names, y = coefs)) +
  geom_point(size = 1) +
  geom_errorbar(aes(ymin = min, ymax = max), width = 0.1) +
  coord_flip() +
  ylab("Effect of lib-cons ideology") +
  xlab("") +
  geom_hline(yintercept = 0) +
  theme_minimal()

print(coef.plot2a_other)
```
# Figure 2b

```{r}
coefs <- unlist(lapply(reg.output.other, function(x) coef(x)["scale(lr)"]))
se    <- unlist(lapply(reg.output.other, function(x) sqrt(diag(vcov(x)))["scale(lr)"]))
min   <- coefs - 1.96 * se
max   <- coefs + 1.96 * se

plot.data <- data.frame(
  names = c("Heads of Government", "Congress NLD"),
  coefs = coefs,
  se = se,
  min = min,
  max = max
)

plot.data$names <- factor(plot.data$names, levels = rev(plot.data$names))

coef.plot2b <- ggplot(plot.data, aes(x = names, y = coefs)) +
  geom_point(size = 1) +
  geom_errorbar(aes(ymin = min, ymax = max), width = 0.1) +
  coord_flip() +
  ylab("Effect of left-right ideology") +
  xlab("") +
  geom_hline(yintercept = 0) +
  theme_minimal()

print(coef.plot2b)
```

# Figure 3B) Time Series Plot - Congress Dutch NLD
673 observations

Need to use fewer breaks, since less length of time...


```{r}
library(ggplot2)

# Keep only Dutch congress speeches
combined.subset <- subset(
  combined_other,
  parliament != "Dutch Congress Speeches"
)

# Create id label
combined.subset$id <- "NLD"

# Make sure year is numeric
combined.subset$year <- as.numeric(combined.subset$year)

# Check Number of Unique Years
length(unique(combined.subset$year))
table(combined.subset$year)

# Plot
time.plot.nld.congress <- ggplot(combined.subset, aes(x = year, y = complexity)) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(
    breaks = c(1990, 2000, 2010),
    labels = c("'90", "'00", "'10")
  ) +
  ylab("Complexity") +
  xlab("") +
  theme_minimal()

print(time.plot.nld.congress)



```
# Figure 4A) Congress NLD only

```{r}
library(ggplot2)

# ---------------------------------
# 1. Create mean-centered year
# ---------------------------------
combined_other$year2 <- combined_other$year - mean(combined_other$year, na.rm = TRUE)

# ---------------------------------
# 2. Keep only Dutch congress speeches
# ---------------------------------
nld_congress <- subset(
  combined_other,
  parliament != "Dutch Congress Speeches"
)


# ---------------------------------
# 3. Fixed-effects model
# ---------------------------------
vars3 <- as.formula(complexity ~ lr + pc + year2 + factor(speaker))

reg.output.fixed.other <- lm(vars3, data = nld_congress)

summary(reg.output.fixed.other)

coefs <- coef(reg.output.fixed.other)["pc"]
se    <- sqrt(diag(vcov(reg.output.fixed.other)))["pc"]
min   <- coefs - 1.96 * se
max   <- coefs + 1.96 * se

plot.data <- data.frame(
  names = "Congress NLD",
  coefs = coefs,
  se = se,
  min = min,
  max = max
)

plot.data$names <- factor(plot.data$names, levels = rev(plot.data$names))

coef.plot4a_nld <- ggplot(plot.data, aes(x = names, y = coefs)) +
  geom_point() +
  geom_errorbar(aes(ymin = min, ymax = max), width = 0.1) +
  coord_flip() +
  ylab("Fixed effect of conservatism") +
  xlab("") +
  geom_hline(yintercept = 0) +
  theme_minimal()

print(coef.plot4a_nld)

```
# Figure 4B)

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)

library(dplyr)
library(tidyr)
library(ggplot2)

# ---------------------------------
# 1. Filter to Dutch congress only
# ---------------------------------
nld_congress <- combined_other %>%
  filter(parliament == "Dutch Congress Speeches") %>%
  mutate(year = as.numeric(year))

# ---------------------------------
# 2. Collapse to yearly means
# ---------------------------------
plot_df <- nld_congress %>%
  group_by(year) %>%
  dplyr::summarise(
    complexity = mean(complexity, na.rm = TRUE),
    ideology   = mean(pc, na.rm = TRUE),
    .groups = "drop"
  )

# ---------------------------------
# 3. Standardize both series
# ---------------------------------
plot_df <- plot_df %>%
  mutate(
    complexity_z = as.numeric(scale(complexity)),
    ideology_z   = as.numeric(scale(ideology))
  )

# ---------------------------------
# 4. Convert to long format
# ---------------------------------
plot_long <- plot_df %>%
  select(year, complexity_z, ideology_z) %>%
  pivot_longer(
    cols = c(complexity_z, ideology_z),
    names_to = "series",
    values_to = "value"
  ) %>%
  mutate(
    series = recode(
      series,
      complexity_z = "complexity",
      ideology_z   = "ideology"
    )
  )

# ---------------------------------
# 5. Plot Figure 4b style
# ---------------------------------
fig4b_nld <- ggplot(plot_long, aes(x = year, y = value, color = series)) +
  geom_smooth(se = FALSE, span = 0.75) +
  labs(
    x = "",
    y = "Standardized values",
    color = ""
  ) +
  theme_minimal()

print(fig4b_nld)
```
## APPENDICES - OTHER COMBINED (HEADS OF GOVERNMENT AND CONGRESS DUTCH)

```{r}
library(dplyr)
library(gt)

combined_other2 <- combined_other %>%
  mutate(
    year = as.numeric(year),
    corpus = case_when(
      parliament == "Heads of Government" ~ "Heads of Government",
      parliament == "Dutch Congress Speeches" ~ "Party congresses NLD",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(corpus))

library(dplyr)
library(gt)
library(webshot2)

# --------------------------------------------------
# 1. PREP DATA
# --------------------------------------------------
combined_other2 <- combined_other %>%
  mutate(
    year = as.numeric(year),
    corpus = case_when(
      parliament == "Heads of Government" ~ "Heads of Government",
      parliament == "Dutch Congress Speeches" ~ "Party congresses NLD",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(corpus))

# --------------------------------------------------
# 2. FUNCTION TO BUILD DESCRIPTIVE TABLE
# --------------------------------------------------
make_desc_table <- function(data, corpus_name) {
  
  vars <- c("complexity", "lr", "pc")
  labels <- c(
    complexity = "Complexity",
    lr = "Left-Right",
    pc = "Progressive-Conservative"
  )
  
  out <- lapply(vars, function(v) {
    x <- data[[v]]
    data.frame(
      Statistic = labels[[v]],
      N = sum(!is.na(x)),
      Mean = mean(x, na.rm = TRUE),
      `St. Dev.` = sd(x, na.rm = TRUE),
      Min = min(x, na.rm = TRUE),
      `Pctl(25)` = quantile(x, 0.25, na.rm = TRUE),
      `Pctl(75)` = quantile(x, 0.75, na.rm = TRUE),
      Max = max(x, na.rm = TRUE),
      check.names = FALSE
    )
  }) %>%
    bind_rows()
  
  gt(out) %>%
    tab_header(
      title = md(corpus_name)
    ) %>%
    fmt_number(
      columns = c(Mean, `St. Dev.`, Min, `Pctl(25)`, `Pctl(75)`, Max),
      decimals = 3
    ) %>%
    fmt_number(
      columns = N,
      decimals = 0
    ) %>%
    cols_align(
      align = "center",
      columns = everything()
    ) %>%
    tab_style(
      style = list(
        cell_text(weight = "bold")
      ),
      locations = cells_title(groups = "title")
    ) %>%
    opt_table_font(
      font = list(
        gt::google_font("Times New Roman"),
        default_fonts()
      )
    ) %>%
    tab_options(
      table.font.size = px(14),
      heading.align = "left",
      column_labels.font.weight = "bold",
      table.border.top.width = px(1),
      table.border.bottom.width = px(1),
      data_row.padding = px(4)
    )
}

# --------------------------------------------------
# 3. BUILD TABLE A.2 = PARTY CONGRESSES NLD
# --------------------------------------------------
table_A2_data <- combined_other2 %>%
  filter(corpus == "Party congresses NLD")

gt_A2 <- make_desc_table(
  data = table_A2_data,
  corpus_name = "Table A.2: Party congresses NLD"
)

gt_A2

# --------------------------------------------------
# 4. BUILD TABLE A.8 = HEADS OF GOVERNMENT
# --------------------------------------------------
table_A8_data <- combined_other2 %>%
  filter(corpus == "Heads of Government")

gt_A8 <- make_desc_table(
  data = table_A8_data,
  corpus_name = "Table A.8: Heads of Government"
)

gt_A8

# --------------------------------------------------
# 5. EXPORT TO PNG / PDF
# --------------------------------------------------
gtsave(gt_A2, "Table_A2_Party_Congresses_NLD.html")

gtsave(gt_A8, "Table_A8_Heads_of_Government.html")

library(dplyr)
library(gt)
library(broom)

library(dplyr)
library(gt)
library(broom)

# --------------------------------------------------
# 1. PREP DATA
# --------------------------------------------------
combined_other2 <- combined_other %>%
  mutate(
    year = as.numeric(year),
    corpus = case_when(
      parliament == "Heads of Government" ~ "Heads of Government",
      parliament == "Dutch Congress Speeches" ~ "Party congresses NLD",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(corpus)) %>%
  mutate(
    year2 = year - mean(year, na.rm = TRUE)
  )

# --------------------------------------------------
# 2. MODEL FUNCTIONS (NO OFFICE)
# --------------------------------------------------
fit_ols_model <- function(df) {
  lm(scale(complexity) ~ scale(lr) + scale(pc) + year2, data = df)
}

fit_fe_model <- function(df) {
  lm(complexity ~ lr + pc + year2 + factor(speaker), data = df)
}

# --------------------------------------------------
# 3. SPLIT DATA
# --------------------------------------------------
df_nld <- combined_other2 %>%
  filter(corpus == "Party congresses NLD")

df_hog <- combined_other2 %>%
  filter(corpus == "Heads of Government")

# --------------------------------------------------
# 4. FIT MODELS
# --------------------------------------------------
mod_C1_nld <- fit_ols_model(df_nld)
mod_C1_hog <- fit_ols_model(df_hog)

mod_D1_nld <- fit_fe_model(df_nld)
mod_D1_hog <- fit_fe_model(df_hog)

# --------------------------------------------------
# 5. FORMAT HELPERS
# --------------------------------------------------
star_p <- function(p) {
  case_when(
    is.na(p) ~ "",
    p < 0.001 ~ "***",
    p < 0.01  ~ "**",
    p < 0.05  ~ "*",
    TRUE ~ ""
  )
}

fmt_coef <- function(est, se, p) {
  if (is.na(est)) return("")
  paste0(
    sprintf("%.3f", est),
    star_p(p),
    "<br>(",
    sprintf("%.3f", se),
    ")"
  )
}

extract_model <- function(model, terms, include_fe = FALSE) {
  td <- broom::tidy(model)
  gl <- broom::glance(model)
  
  out <- sapply(terms, function(term_name) {
    row <- td[td$term == term_name, ]
    if (nrow(row) == 0) return("")
    fmt_coef(row$estimate[1], row$std.error[1], row$p.value[1])
  })
  
  out <- as.list(out)
  
  out[["Speaker fixed effects"]] <- if (include_fe) "Yes" else "No"
  out[["N"]] <- formatC(gl$nobs[1], format = "d", big.mark = ",")
  out[["R²"]] <- sprintf("%.3f", gl$r.squared[1])
  out[["Adj. R²"]] <- sprintf("%.3f", gl$adj.r.squared[1])
  
  out
}

# --------------------------------------------------
# 6. TERMS
# --------------------------------------------------
terms_C1 <- c("scale(lr)", "scale(pc)", "year2")
terms_D1 <- c("lr", "pc", "year2")

row_names <- c(
  "Left-Right",
  "Progressive-Conservative",
  "Year",
  "Speaker fixed effects",
  "N",
  "R²",
  "Adj. R²"
)

# --------------------------------------------------
# 7. TABLE C.1 (OLS)
# --------------------------------------------------
col_C1_nld <- extract_model(mod_C1_nld, terms_C1, include_fe = FALSE)
col_C1_hog <- extract_model(mod_C1_hog, terms_C1, include_fe = FALSE)

table_C1 <- data.frame(
  Term = row_names,
  `Party congresses NLD` = unname(unlist(col_C1_nld)),
  `Heads of Government` = unname(unlist(col_C1_hog)),
  check.names = FALSE
)

gt_C1 <- gt(table_C1) %>%
  tab_header(
    title = md("**Table C.1. OLS models: Combined other corpora**")
  ) %>%
  fmt_markdown(columns = -Term) %>%
  cols_align(align = "center", columns = -Term) %>%
  cols_align(align = "left", columns = Term) %>%
  tab_source_note(
    source_note = md("* p < .05, ** p < .01, *** p < .001")
  )

gt_C1

# --------------------------------------------------
# 8. TABLE D.1 (FE MODELS)
# --------------------------------------------------
col_D1_nld <- extract_model(mod_D1_nld, terms_D1, include_fe = TRUE)
col_D1_hog <- extract_model(mod_D1_hog, terms_D1, include_fe = TRUE)

table_D1 <- data.frame(
  Term = row_names,
  `Party congresses NLD` = unname(unlist(col_D1_nld)),
  `Heads of Government` = unname(unlist(col_D1_hog)),
  check.names = FALSE
)

gt_D1 <- gt(table_D1) %>%
  tab_header(
    title = md("**Table D.1. Speaker fixed-effects models: Combined other corpora**")
  ) %>%
  fmt_markdown(columns = -Term) %>%
  cols_align(align = "center", columns = -Term) %>%
  cols_align(align = "left", columns = Term) %>%
  tab_source_note(
    source_note = md("* p < .05, ** p < .01, *** p < .001")
  )

gt_D1

# --------------------------------------------------
# 9. SAVE (NO CHROME NEEDED)
# --------------------------------------------------
gtsave(gt_C1, "Table_C1.html")
gtsave(gt_D1, "Table_D1.html")

```

